The \dealii Library, Version 9.5

### 2023-07-06 9.5/paper.tex
write second CMake paragraph

\todo[inline]{Matthias: Write?}

>>>>

\dealii's CMake project configuration itself now exports three targets,
\texttt{dealii::dealii\_debug}, \texttt{dealii::dealii\_release}, and
\texttt{dealii::dealii}. Linking against one of the first two variants via
\texttt{target\_link\_libraries()} populates the target with all necessary
include directories and the full link interface necessary for \dealii. The
third variant, \texttt{dealii::dealii}, automatically switches between
debug and release interface depending on the build type set via
\texttt{CMAKE\_BUILD\_TYPE}. The \texttt{dealii::dealii} third variant also
populates compiler and linker options, whereas for the first two variants a
client project has to ensure that the compiler and linker are properly set
up. The new import targets make it now possible to configure a dependent
project without the use of any \dealii specific macros:
%
\begin{anycode}
cmake_minimum_required(VERSION 3.13.4)
set(CMAKE_BUILD_TYPE Debug CACHE STRING "")
project(step CXX)

find_package(deal.II 9.5.0 REQUIRED)

add_executable(step step.cc)
target_link_libraries(step dealii::dealii)
\end{anycode}
